The regularity of ODEs and thimble integrals \\ with respect to Borel summation

### 2025-08-27 SIGMA/borel-regularity-SIGMA.tex
Start correcting the triangular cantilever example

% highlightable revisions
\newif\ifhighlightrevs
\highlightrevstrue
\ifhighlightrevs
\newenvironment{revised}{\color{DarkBlue}}{\color{black}}
\else
\newenvironment{revised}{}{}
\fi

@@

The particular classes of problems we look at are level~1 ODEs and exponential period integrals over one dimensional Lefschetz thimbles. To expand the variety of examples available in the literature, we treat various examples of these problems in detail.
\end{abstract}
\tableofcontents
%
\section{Introduction}
%
\subsection{The unreasonable effectiveness of Borel summation}\label{intro:summation}
You can often find a formal power series
\[ \series{\Phi} = \frac{c_0}{z^\tau} + \frac{c_1}{z^{\tau+1}} + \frac{c_2}{z^{\tau+2}} + \frac{c_3}{z^{\tau+3}} + \ldots, \]
with $\tau \in (0, 1]$, that looks or acts like a solution to a problem whose actual solutions are holomorphic functions of $z$. For example, if you want to understand how the solutions of the holomorphic ordinary differential equation (ODE)
\begin{equation}
\left[ \big[ \big(\tfrac{\partial}{\partial z}\big)^2 - 1 \big] + z^{-1} \tfrac{\partial}{\partial z} - \big(\tfrac{1}{3}\big)^2 z^{-2} \right] \Phi= 0. \label{eqn:bessel_rescaled_ex}
\end{equation}
behave near $z = \infty$, you might start by looking for formal {\em trans-monomial} solutions $e^{-\alpha z}\,\series{\Phi}$, where $\series{\Phi}$ is a formal power series of the kind above. Setting $\alpha = -1$ and $\tau = \tfrac{1}{2}$ gives a well-behaved recurrence relation for $\series{\Phi}$, which produces the solution 
\begin{equation}
e^{z} \left[ \frac{(-1)!!}{z^{1/2}} + \frac{5}{72} \cdot \frac{1!!}{z^{3/2}} + \frac{385}{31104} \cdot \frac{3!!}{z^{5/2}} + \frac{17017}{6718464} \cdot \frac{5!!}{z^{7/2}} + \ldots \right] \label{series:bessel_ex}
\end{equation}
and its constant multiples (see \cite[equation 10.40.1]{dlmf}). As another example, you might rewrite the integral
\begin{equation}\label{int:bessel_ex}
\Phi = \int_{\mathcal{C}} \exp\left[-z \left(4 u^3 - 3 u\right)\right]\,du
\end{equation}
as \begin{verify}[see \texttt{notes/intro series computation.nb} and \texttt{notes/intro series computation.ipynb}]\end{verify}
\[ e^{z}\, \frac{1}{2\sqrt{3}}\, \int_{-\infty}^\infty e^{-z t^2/2} \left[ 1 - \frac{\sqrt{3}}{9} t + \frac{5}{72} t^2 - \frac{4\sqrt{3}}{243} t^3 + \frac{385}{31104} t^4 - \frac{7\sqrt{3}}{2187} t^5 + \frac{17017}{6718464} t^6 - \ldots \right] dt \]
using the substitution $\tfrac{1}{2} t^2 = 4u^3 - 3u + 1$. Na\"{i}vely integrating term by term, you again get the transmonomial~\eqref{series:bessel_ex}, up to a constant.

Once you have the formal solution $\series{\Phi}$, you might try to get an actual solution by applying {\em Borel summation}, which turns a formal power series into a function asymptotic to it. Borel summation works in three steps.
\begin{enumerate}
\item Thinking of $z$ as a ``frequency variable,'' we take the Borel transform (also known as formal inverse Laplace transform) of $\series{\Phi}$, producing a formal power series $\series{\phi}$ in a new ``position variable'' $\zeta$.
\item If $\series{\phi}$ has a positive radius of convergence, we sum it to get a holomorphic function $\hat{\phi}$ on a neighbourhood of $\zeta = 0$. Then, by analytic continuation, we expand the domain of $\hat{\phi}$ to a Riemann surface $B$ with a distinguished 1-form $\lambda$---the continuation of $d\zeta$.
\item If $\hat{\phi}$ grows slowly enough along an infinite ray $\zeta \in \alpha + e^{i\theta}(0, \infty)$, its Laplace transform $\hat{\Phi} := \laplace_{\zeta, \alpha}^\theta \hat{\phi}$ turns out to be a holomorphic function of $z$, well-defined on some sector of the frequency plane. In this case, we say $\series{\Phi}$ is {\em Borel summable}, and we call $\hat{\Phi}$ its {\em Borel sum} at $\alpha$ in the direction $\theta$.
\end{enumerate}
\begin{center}
\basicLaplace
\captionof{figure}{The Laplace transform $\laplace^\theta_{\zeta, \alpha}$ integrates a function along the ray $\zeta \in \alpha + e^{i\theta}(0, \infty)$ in the position domain, turning it into a function on some half-plane $\Re(e^{i\theta} z) > \Lambda$ in the frequency domain.}
\end{center}

@@

If two power series of the form \eqref{series:asymp-definition} are asymptotic to the same function, they must be equal; this can be deduced from the triangle inequality. The power series which is asymptotic to a given function on a given open sector, if it exists, is therefore an intrinsic property of the function: we call it the function's {\em asymptotic expansion} on that sector. The functions that have asymptotic expansions on a given sector form a ring~\cite[Section~A.4]{nikolaev2023existence}, and the map that sends such a function to its asymptotic expansion is a ring homomorphism. Since asymptotic expansions on overlapping sectors must agree, we can think of this homomorphism as being determined by a ray.
\begin{definition}
For any direction $\theta$ and any trans-monomial space $e^{\alpha z} z^{-\sigma} \C \llbracket z^{-1} \rrbracket$, the {\em asymptotic expansion} homomorphism
\[ \aexp^\theta \maps \mathcal{O}(\C) \to e^{\alpha z} z^{-\sigma} \C \llbracket z^{-1} \rrbracket \]
is the partially defined map that sends a holomorphic function on an open subset of $\C$ to its asymptotic expansion on a sector containing the end of the ray $z \in e^{i\theta}(0, \infty)$. To be in the domain of $\aexp^\theta$, a function just needs to have an asymptotic expansion on one such sector.
\end{definition}
\begin{definition}\label{def:unif-gevrey-asymp}
On an open sector $\Omega$ around $\infty$, a holomorphic function $\Phi$ is {\em uniformly $1$-Gevrey asymptotic} to a power series of the form \eqref{series:asymp-definition} if there is a constant $A \in (0, \infty)$ for which
\[ \left|\Phi - \left(a_0 + \frac{a_1}{z} + \frac{a_2}{z^2} + \ldots + \frac{a_{n-1}}{z^{n-1}} \right) \right| \lesssim \frac{A^n n!}{|z|^n} \]
over all orders $n$ and all $z \in \Omega$. We will use $\lesssim$ throughout the paper to mean ``bounded by a constant multiple of,'' with the same constant over all the specified variables.
\end{definition}
To compare the Borel sum $\hat{\Phi}$ with the original series $\series{\Phi}$, let us take it one more step, sending it back into the world of formal power series by taking its asymptotic expansion.

\begin{enumerate}[start=4]
\item By construction, $\aexp^\theta \hat{\Phi} = \series{\Phi}$. It turns out that $\hat{\Phi}$ is not only asymptotic to $\series{\Phi}$, but {\em {uniformly} $1$-Gevrey}-asymptotic~\cite[Corollary~5.23]{diverg-resurg-i}.
\end{enumerate}

The Borel summation process is summarized in the following diagram:
\begin{center}
\begin{tikzcd}
& \text{problem} & \\
\hat{\Phi} \arrow[ru, dotted, no head, tail] \arrow[rr, mapsto, "\aexp^\theta", "\text{($1$-Gevrey)}"'] & & \series{\Phi} \arrow[lu, no head, tail, "\parbox{10mm}{\centering\scriptsize formally solves}"'] \arrow[dd, mapsto, "\borel"] \\
& & \\
\hat{\phi} \arrow[uu, mapsto, "\laplace_b^\theta"] & & \series{\phi} \arrow[ll, mapsto, "\text{sum}"] 
\end{tikzcd}
\end{center}

You can not be sure {\em a priori} that $\hat{\Phi}$ solves your original problem, even if you know that $\series{\Phi}$ is asymptotic to an actual solution. After all, $\series{\Phi}$ is asymptotic to many functions; Borel summation simply picks one of them. In many cases, however, Borel summation picks correctly, delivering an actual solution to your problem. The question of how that happens is the starting point for this paper.
%
\subsection{A new perspective: Borel regularity}
%
\subsubsection{Introducing Borel regularity}
%
We will look at the effectiveness of Borel summation from an analytic perspective, as a regularity property of problems and their holomorphic solutions. Suppose we have a holomorphic function $\Phi$ which is a solution of some problem. If the asymptotic expansion $\series{\Phi} = \ae^\theta \Phi$ is well-defined, it should be a formal solution of the same problem; we can take this as a basic requirement for our concept of a formal solution.
\begin{center}
\begin{tikzcd}
& \text{problem} & \\
\Phi \arrow[ru, no head, tail, swap, "\text{solves}"' ] \arrow[rrd, mapsto, "\aexp^{\theta}"]& & \\
\hat{\Phi} \arrow[rr, "\aexp^{\theta}", "\text{($1$-Gevrey)}"'] & & \series{\Phi} \arrow[luu, no head, tail, swap, "\parbox{10mm}{\centering\scriptsize formally solves}"] \arrow[dd, mapsto, "\borel_\zeta"] \\
& & \\
\hat{\phi} \arrow[uu, mapsto, "\laplace_{\zeta, 0}^\theta"] & & \series{\phi} \arrow[ll, mapsto, "\text{sum}"] 
\end{tikzcd}
\end{center}
If $\series{\Phi}$ is Borel summable, as described in Section~\ref{intro:summation}, its Borel sum $\hat{\Phi}$ is a new holomorphic function.
Since different functions can have the same asymptotic expansion, taking the Borel sum of the asymptotic expansion of a function must smooth away some details. We will therefore call this process {\em Borel regularization}. Explicitly, Borel regularization works in four steps:
\begin{enumerate}
\item Take the asymptotic expansion $\series{\Phi} = \aexp^{-\theta} \Phi$.
\item Take the Borel transform $\series{\phi} = \borel_\zeta \series{\Phi}$.
\item Take the sum $\hat{\phi}$ of $\series{\phi}$, and expand its domain to a Riemann surface with a distinguished $1$-form, as before.
\item Take the Laplace transform $\hat{\Phi} = \laplace_{\zeta, 0}^\theta \hat{\phi}$. This is possible, by definition, if $\series{\Phi}$ is Borel summable.\footnote{More generally, we could take the Laplace transform $\laplace^\theta_{\zeta, \alpha}$ starting at any point $\zeta = \alpha$ in $B$. The choice of starting point will play an important role in our study of ODEs and thimble integrals.}
\end{enumerate}
We will say a function is {\em Borel regularizable} if its asymptotic expansion is well-defined and Borel summable, ensuring that we can carry out all the steps.

@@

The central goal of this paper is to explain, from this perspective, why Borel summation works well for the two kinds of problems exemplified in Section~\ref{intro:summation}.
\begin{enumerate}
\item Solving a level~$1$ linear ODE \cite[Section 2.1]{EcalleIII}\cite[Section~5.2.2.1]{diverg-resurg-iii}. Equation~\eqref{eqn:bessel_rescaled_ex} is an example. More generally, we will consider equations of the form $\mathcal{P} \Phi = 0$ given by a differential operator of the form 
\[ \mathcal{P} = P\big(\tfrac{\partial}{\partial z}\big) + \frac{1}{z} Q\big(\tfrac{\partial}{\partial z}\big) + \frac{1}{z^2} R(z^{-1}), \]
where $P$ is a monic degree-$d$ polynomial, $Q$ is a degree-$(d-1)$ polynomial that is non-zero at every root of $P$, and $R(z^{-1})$ is holomorphic in some disk $|z| > A$ around $z = \infty$. We will restrict our attention to the case where the roots of $P$ are simple (see Section \ref{borel_reg-ODE}), and to the solutions associated with roots $-\alpha$ where $\tau_\alpha:=\frac{Q(-\alpha)}{P'(-\alpha)}$ is real and positive (see Theorem~\ref{thm:exist_uniq_ODE}).

The form of $\mathcal{P}$ derives from equation~2.2.3 of \cite[p.~105]{EcalleIII}, which encompasses both linear and nonlinear ODEs of level $1$. Borel summation is more involved for the nonlinear ones, raising the question of whether our analysis generalizes.
%
\item Evaluating a one-dimensional {\em thimble integral}. Integral~\eqref{int:bessel_ex} is an example. More generally, we will consider integrals of the form
\begin{equation*}
I = \int_{\mathcal{C}}e^{-zf}\,\nu,
\end{equation*}
where $X$ is $1$-dimensional complex manifold; $f \maps X \to \C$ is a holomorphic function with isolated, non-degenerate critical points; $\nu \in \Omega^1(X)$ is holomorphic $1$-form on $X$, and $\mathcal{C}$ is {\em Lefschetz thimble}---a type of contour described in Section~\ref{sec:why_borel_thimble}. Under these conditions, $I$ is a holomorphic function of $z$.
\end{enumerate}
These two problems are closely linked. By playing with derivatives of a thimble integral, you can often find a linear ODE that the integral satisfies. Conversely, for many classical ODEs, there are useful bases of thimble integral solutions.
%
\subsection{Goals and Results}
%
We present the results, proofs, and examples in this paper with a few central goals in mind. Our first goal is to discuss Borel summability in a way that carefully separates the analytic and formal sides of the theory. In particular, we highlight results that can be proven in purely analytic ways, like Theorem~\ref{thm:exist_uniq_ODE} for level~1 ODEs and Lemma~\ref{lem:thimble_proj_formula} for thimble integrals.

@@

Our third goal is to illustrate the results we discuss with detailed examples involving a diversity of Borel regular functions. We treat several examples both as thimble integrals and as solutions of level~1 ODEs, so you can compare these parallel explanations of how Borel regularity arises. We include ODEs of both second degree and higher degree. Using the widely discussed example of the Airy function, we compare our treatment with other approaches and conventions found in the literature.

We state our main results in Sections~\ref{sec:why_borel_ODE}--\ref{sec:why_borel_thimble} and prove them in Section~\ref{sec:proof_main_results}. Our examples are in Section~\ref{sec:examples}. Section~\ref{sec:org} describes the layout of the paper in more detail.
%
\subsubsection{Why does Borel summation work for solutions of level $1$ ODEs?}\label{sec:why_borel_ODE}
%
Consider a linear level-$1$ differential operator $\mathcal{P}$ of the form described in~Section~\ref{borel-reg:explanatory-power}. This operator will always have an irregular singularity at $z = \infty$.
\begin{verify}
\par
Turn the ODE into a system: assume 
\begin{align*}
P(\lambda) & = P_0 + P_1 \lambda + \ldots + P_d \lambda^d \\
Q(\lambda) & = Q_0 + Q_1 \lambda + \ldots + Q_{d-1} \lambda^{d-1}
\end{align*}
then the ODE $\mathcal{P}\psi=0$ is equivalent to the system 
    \begin{equation}
        \frac{d}{dz}Y= B(z) Y 
    \end{equation}
    \[
    B(z)=\begin{pmatrix}
            0 & 1 & 0 & \ldots & 0 \\
            0 & 0 & 1 & \ldots & 0 \\
            \vdots & &\ddots & & 1\\
            b_{1}(z) & & b_j(z) & \ldots & b_{d-1}(z)
        \end{pmatrix}, \quad Y=\begin{pmatrix}
            \psi \\
            \psi ' \\
            \vdots \\
            \psi^{(d-1)}
        \end{pmatrix}
    \]

@@

and $-w^{-2}B(1/w)$ has a simple pole at $w=0$ (i.e. $z=\infty$). Then the formal system of solutions is of the form 
\[\psi_j(w)=e^{-\alpha_j/w} w^{\tau_j} \tilde{f}_j(w)\]
hence according to \cite[Definition 3.3.2]{diverg-resurg--ii}, $w=0$ is irregular.
\par
\end{verify}
We can find holomorphic solutions of the equation $\mathcal{P}\Phi = 0$ by taking the Borel sums of formal trans-monomial solutions. However, this only works when there is a coincidence between exponential factor $e^{-\alpha z}$ in the formal solution, the base point $\zeta = \alpha$ we use for Borel summation, and the characteristic equation $P(-\alpha) = 0$. Why?

A first clue is the observation that every solution we get from Borel summation is, by definition, the Laplace transform $\Phi = \laplace_{\zeta,\alpha}^\theta \phi$ of a function on $\phi$ the position domain. In fact, the differential equation $\mathcal{P}\Phi = 0$ is equivalent to an integral equation $\hat{\mathcal{P}}_\alpha \phi = 0$.

>>>>

% highlightable revisions
\newif\ifhighlightrevs
\highlightrevstrue
\ifhighlightrevs
\newenvironment{revised}{\color{OrangeRed}}{\color{black}}
\else
\newenvironment{revised}{}{}
\fi

@@

The particular classes of problems we look at are level~$1$ ODEs and exponential period integrals over \begin{revised}one-dimensional\end{revised} Lefschetz thimbles. To expand the variety of examples available in the literature, we treat various examples of these problems in detail.
\end{abstract}
\tableofcontents
%
\section{Introduction}
%
\subsection{The unreasonable effectiveness of Borel summation}\label{intro:summation}
You can often find a formal power series
\[ \series{\Phi} = \frac{c_0}{z^\tau} + \frac{c_1}{z^{\tau+1}} + \frac{c_2}{z^{\tau+2}} + \frac{c_3}{z^{\tau+3}} + \ldots, \]
with $\tau \in (0, 1]$, that looks or acts like a solution to a problem whose actual solutions are holomorphic functions of $z$. For example, if you want to understand how the solutions of the holomorphic ordinary differential equation (ODE)
\begin{equation}
\left[ \big[ \big(\tfrac{\partial}{\partial z}\big)^2 - 1 \big] + z^{-1} \tfrac{\partial}{\partial z} - \big(\tfrac{1}{3}\big)^2 z^{-2} \right] \Phi= 0. \label{eqn:bessel_rescaled_ex}
\end{equation}
behave near $z = \infty$, you might start by looking for formal {\em trans-monomial} solutions $e^{-\alpha z}\,\series{\Phi}$, where $\series{\Phi}$ is a formal power series of the kind above.\footnote{\begin{revised} Trans-mononials can be of different kind, for example fractional powers of $z$ can appear at the exponent. In this paper we will only deal with trans-monomial of the form $e^{-\alpha z}$, for some $\alpha\in\C$.\end{revised}} Setting $\alpha = -1$ and $\tau = \tfrac{1}{2}$ gives a well-behaved recurrence relation for $\series{\Phi}$, which produces the solution 
\begin{equation}
e^{z} \left[ \frac{(-1)!!}{z^{1/2}} + \frac{5}{72} \cdot \frac{1!!}{z^{3/2}} + \frac{385}{31104} \cdot \frac{3!!}{z^{5/2}} + \frac{17017}{6718464} \cdot \frac{5!!}{z^{7/2}} + \ldots \right] \label{series:bessel_ex}
\end{equation}
and its constant multiples (see \cite[equation 10.40.1]{dlmf}). As another example, you might rewrite the integral
\begin{equation}\label{int:bessel_ex}
\Phi = \int_{\mathcal{C}} \exp\left[-z \left(4 u^3 - 3 u\right)\right]\,du
\end{equation}
as \begin{verify}[see \texttt{notes/intro series computation.nb} and \texttt{notes/intro series computation.ipynb}]\end{verify}
\[ e^{z}\, \frac{1}{2\sqrt{3}}\, \int_{-\infty}^\infty e^{-z t^2/2} \left[ 1 - \frac{\sqrt{3}}{9} t + \frac{5}{72} t^2 - \frac{4\sqrt{3}}{243} t^3 + \frac{385}{31104} t^4 - \frac{7\sqrt{3}}{2187} t^5 + \frac{17017}{6718464} t^6 - \ldots \right] dt \]
using the substitution $\tfrac{1}{2} t^2 = 4u^3 - 3u + 1$. Na\"{i}vely integrating term by term, you again get the \begin{revised}trans-monomial\end{revised}~\eqref{series:bessel_ex}, up to a constant.

Once you have the formal solution $\series{\Phi}$, you might try to get an actual solution by applying {\em Borel summation}, which turns a formal power series into a function asymptotic to it. Borel summation works in three steps.
\begin{enumerate}
\item Thinking of $z$ as a ``frequency variable,'' we take the Borel transform (also known as formal inverse Laplace transform) of $\series{\Phi}$, producing a formal power series $\series{\phi}$ in a new ``position variable'' $\zeta$.
\item If $\series{\phi}$ has a positive radius of convergence, we sum it to get a holomorphic function $\hat{\phi}$ on a \begin{revised}neighborhood\end{revised} of $\zeta = 0$. Then, by analytic continuation, we expand the domain of $\hat{\phi}$ to a Riemann surface $B$ with a distinguished 1-form $\lambda$\begin{revised},\end{revised} the continuation of $d\zeta$.
\item If $\hat{\phi}$ grows slowly enough along an infinite ray $\zeta \in \alpha + e^{i\theta}(0, \infty)$, its Laplace transform $\hat{\Phi} := \laplace_{\zeta, \alpha}^\theta \hat{\phi}$ turns out to be a holomorphic function of $z$, well-defined on some sector of the frequency plane. In this case, we say $\series{\Phi}$ is {\em Borel summable}, and we call $\hat{\Phi}$ its {\em Borel sum} at $\alpha$ in the direction $\theta$.
\end{enumerate}
\begin{center}
\basicLaplace
\captionof{figure}{The Laplace transform $\laplace^\theta_{\zeta, \alpha}$ integrates a function along the ray $\zeta \in \alpha + e^{i\theta}(0, \infty)$ in the position domain, turning it into a function on some half-plane $\Re(e^{i\theta} z) > \Lambda$ in the frequency domain.}
\end{center}

@@

\begin{revised}If a function is asymptotic to two power series of the form \eqref{series:asymp-definition}, those series must be equal;\end{revised}
\begin{old}If two power series of the form \eqref{series:asymp-definition} are asymptotic to the same function, they must be equal;\end{old} this can be deduced from the triangle inequality. The power series which \begin{old}is asymptotic to\end{old} a given function \begin{revised}is asymptotic to\end{revised} on a given open sector, if it exists, is therefore an intrinsic property of the function: we call it the function's {\em asymptotic expansion} on that sector. The functions that have asymptotic expansions on a given sector form a ring~\cite[Section~A.4]{nikolaev2023existence}, and the map that sends such a function to its asymptotic expansion is a ring homomorphism. Since asymptotic expansions on overlapping sectors must agree, we can think of this homomorphism as being determined by a ray.
\begin{definition}
For any direction $\theta$ and any trans-monomial space $e^{\alpha z} z^{-\sigma} \C \llbracket z^{-1} \rrbracket$, the {\em asymptotic expansion} homomorphism
\[ \aexp^\theta \maps \mathcal{O}(\C) \to e^{\alpha z} z^{-\sigma} \C \llbracket z^{-1} \rrbracket \]
is the partially defined map that sends a holomorphic function on an open subset of $\C$ to its asymptotic expansion on a sector containing the end of the ray $z \in e^{i\theta}(0, \infty)$. To be in the domain of $\aexp^\theta$, a function just needs to have an asymptotic expansion on one such sector.
\end{definition}
\begin{definition}\label{def:unif-gevrey-asymp}
On an open sector $\Omega$ around $\infty$, a holomorphic function $\Phi$ is {\em uniformly $1$-Gevrey asymptotic} to a power series of the form \eqref{series:asymp-definition} if there is a constant $A \in (0, \infty)$ for which
\[ \left|\Phi - \left(a_0 + \frac{a_1}{z} + \frac{a_2}{z^2} + \ldots + \frac{a_{n-1}}{z^{n-1}} \right) \right| \lesssim \frac{A^n n!}{|z|^n} \]
over all orders $n$ and all $z \in \Omega$. We will use $\lesssim$ throughout the paper to mean ``bounded by a constant multiple of,'' with the same constant over all the specified variables.
\end{definition}
To compare the Borel sum $\hat{\Phi}$ with the original series $\series{\Phi}$, let us take it one more step, sending it back into the world of formal power series by taking its asymptotic expansion.

\begin{enumerate}[start=4]
\item By construction, $\begin{revised}\aexp^{-\theta}\end{revised} \hat{\Phi} = \series{\Phi}$. It turns out that $\hat{\Phi}$ is not only asymptotic to $\series{\Phi}$, but {\em {uniformly} $1$-Gevrey}-asymptotic~\cite[Corollary~5.23]{diverg-resurg-i}.
\end{enumerate}

The Borel summation process is summarized in the following diagram:
\begin{center}
\begin{tikzcd}
& \text{problem} & \\
\hat{\Phi} \arrow[ru, dotted, no head, tail] \arrow[rr, mapsto, "\begin{revised}\aexp^{-\theta}\end{revised}", "\text{($1$-Gevrey)}"'] & & \series{\Phi} \arrow[lu, no head, tail, "\parbox{10mm}{\centering\scriptsize formally solves}"'] \arrow[dd, mapsto, "\borel"] \\
& & \\
\hat{\phi} \arrow[uu, mapsto, "\laplace_b^\theta"] & & \series{\phi} \arrow[ll, mapsto, "\text{sum}"] 
\end{tikzcd}
\end{center}

You can not be sure {\em a priori} that $\hat{\Phi}$ solves your original problem, even if you know that $\series{\Phi}$ is \begin{revised}the asymptotic expansion of\end{revised} an actual solution. After all, $\series{\Phi}$ is asymptotic to many functions; Borel summation simply picks one of them. In many cases, however, Borel summation picks correctly, delivering an actual solution to your problem. \begin{revised}Borel recognized this phenomenon as a key motivation for the study of divergent series \cite{borel-memoire,borel-lecons}, and much has been said about it since (Section~\ref{sec:historical-context});\end{revised} \begin{revised}the\end{revised} question of how \begin{revised}it\end{revised} happens is the starting point for this paper.
%
\subsection{A new perspective: Borel regularity}
%
\subsubsection{Introducing Borel regularity}
%
We will look at the effectiveness of Borel summation from an analytic perspective, as a regularity property of problems and their holomorphic solutions. Suppose we have a holomorphic function $\Phi$ which is a solution of some problem. If the asymptotic expansion $\series{\Phi} = \ae^{-\theta} \Phi$ is well-defined, it should be a formal solution of the same problem; we can take this as a basic requirement for our concept of a formal solution.
\begin{center}
\begin{tikzcd}
& \text{problem} & \\
\Phi \arrow[ru, no head, tail, swap, "\text{solves}"' ] \arrow[rrd, mapsto, "\aexp^{\begin{revised}-\end{revised}\theta}"]& & \\
\hat{\Phi} \arrow[rr, "\aexp^{\begin{revised}-\end{revised}\theta}", "\text{($1$-Gevrey)}"'] & & \series{\Phi} \arrow[luu, no head, tail, swap, "\parbox{10mm}{\centering\scriptsize formally solves}"] \arrow[dd, mapsto, "\borel_\zeta"] \\
& & \\
\hat{\phi} \arrow[uu, mapsto, "\laplace_{\zeta, 0}^\theta"] & & \series{\phi} \arrow[ll, mapsto, "\text{sum}"] 
\end{tikzcd}
\end{center}
If $\series{\Phi}$ is Borel summable, as described in Section~\ref{intro:summation}, its Borel sum $\hat{\Phi}$ is a new holomorphic function.
Since different functions can have the same asymptotic expansion, taking the Borel sum of the asymptotic expansion of a function must smooth away some details. We will therefore call this process {\em Borel regularization}. Explicitly, Borel regularization works in four steps:
\begin{enumerate}
\item Take the asymptotic expansion $\series{\Phi} = \aexp^{-\theta} \Phi$.\footnote{\begin{revised}The choice of $-\theta$ in the asymptotic expansion is dictated by our convention for the Laplace transform that we decide to take in direction $\theta$, like we do in step $4.$. As explained in Section~2.1, the sign of the angle $\theta$ should be consistent between the asymptotic expansion and the Laplace transform.\end{revised}}
\item Take the Borel transform $\series{\phi} = \borel_\zeta \series{\Phi}$.
\item Take the sum $\hat{\phi}$ of $\series{\phi}$, and expand its domain to a Riemann surface \begin{revised}$B$\end{revised} with a distinguished $1$-form, as before.
\item Take the Laplace transform $\hat{\Phi} = \laplace_{\zeta, 0}^\theta \hat{\phi}$. This is possible, by definition, if $\series{\Phi}$ is Borel summable.\footnote{More generally, we could take the Laplace transform $\laplace^\theta_{\zeta, \alpha}$ starting at any point $\zeta = \alpha$ in $B$. The choice of starting point will play an important role in our study of ODEs and thimble integrals.}
\end{enumerate}
We will say a function is {\em Borel regularizable} if its asymptotic expansion is well-defined and Borel summable, ensuring that we can carry out all the steps.

@@

The central goal of this paper is to explain, from this perspective, why Borel summation works well for the two kinds of problems exemplified in Section~\ref{intro:summation}.
\begin{enumerate}
\item Solving a level~$1$\footnote{\begin{revised}The level of linear ODE at a singular point is defined by looking at the Newton polygon associated to the equation, and it corresponds to its positive slope~\cite[Proposition~3.3.14]{diverg-resurg--ii} \end{revised}} linear ODE \cite[Section 2.1]{EcalleIII}\cite[Section~5.2.2.1]{diverg-resurg-iii}. Equation~\eqref{eqn:bessel_rescaled_ex} is an example. More generally, we will consider equations of the form $\mathcal{P} \Phi = 0$ given by a differential operator of the form 
\[ \mathcal{P} = P\big(\tfrac{\partial}{\partial z}\big) + \frac{1}{z} Q\big(\tfrac{\partial}{\partial z}\big) + \frac{1}{z^2} R(z^{-1}), \]
where $P$ is a monic degree-$d$ polynomial, $Q$ is a degree-$(d-1)$ polynomial that is non-zero at every root of $P$, and $R(z^{-1})$ is holomorphic in some disk $|z| > A$ around $z = \infty$. We will restrict our attention to the case where the roots of $P$ are simple (see Section \ref{borel_reg-ODE}), and to the solutions associated with roots $-\alpha$ where $\tau_\alpha:=\frac{Q(-\alpha)}{P'(-\alpha)}$ is real and positive (see Theorem~\ref{thm:exist_uniq_ODE}).

The form of $\mathcal{P}$ derives from equation~2.2.3 of \cite[p.~105]{EcalleIII}, which encompasses both linear and nonlinear ODEs of level $1$. Borel summation is more involved for the nonlinear ones, raising the question of whether our analysis generalizes.
%
\item Evaluating a one-dimensional {\em thimble integral}. Integral~\eqref{int:bessel_ex} is an example. More generally, we will consider integrals of the form
\begin{equation*}
I = \int_{\mathcal{C}}e^{-zf}\,\nu,
\end{equation*}
where $X$ is one-dimensional complex manifold; $f \maps X \to \C$ is a holomorphic function with isolated, non-degenerate critical points; $\nu \in \Omega^1(X)$ is holomorphic $1$-form on $X$, and $\mathcal{C}$ is {\em Lefschetz thimble}---a type of contour described in Section~\ref{sec:why_borel_thimble}. Under these conditions, $I$ is a holomorphic function of $z$.
\end{enumerate}
These two problems are closely linked. By playing with derivatives of a thimble integral, you can often find a linear ODE that the integral satisfies. Conversely, for many classical ODEs, there are useful bases of thimble integral solutions.
%
\subsection{Goals and Results}
%
We present the results, proofs, and examples in this paper with a few central goals in mind. Our first goal is to discuss Borel summability in a way that carefully separates the analytic and formal sides of the theory. In particular, we highlight results that can be proven in purely analytic ways, like Theorem~\ref{thm:exist_uniq_ODE} for level~$1$ ODEs and Lemma~\ref{lem:thimble_proj_formula} for thimble integrals.

@@

Our third goal is to illustrate the results we discuss with detailed examples involving a diversity of Borel regular functions. We treat several examples both as thimble integrals and as solutions of level~$1$ ODEs, so you can compare these parallel explanations of how Borel regularity arises. We include ODEs of both second degree and higher degree. Using the widely discussed example of the Airy function, we compare our treatment with other approaches and conventions found in the literature.

We state our main results in Sections~\ref{sec:why_borel_ODE}--\ref{sec:why_borel_thimble} and prove them in Section~\ref{sec:proof_main_results}. Our examples are given in Section~\ref{sec:examples}. Section~\ref{sec:org} describes the layout of the paper in more detail.
%
\subsubsection{Why does Borel summation work for solutions of level $1$ ODEs?}\label{sec:why_borel_ODE}
%
Consider a linear level~$1$ differential operator $\mathcal{P}$ of the form described in~Section~\ref{borel-reg:explanatory-power}. This operator will always have an irregular singularity at $z = \infty$.
\begin{verify}
\par
Turn the ODE into a system: assume 
\begin{align*}
P(\lambda) & = P_0 + P_1 \lambda + \ldots + P_d \lambda^d \\
Q(\lambda) & = Q_0 + Q_1 \lambda + \ldots + Q_{d-1} \lambda^{d-1}
\end{align*}
then the ODE $\mathcal{P}\psi=0$ is equivalent to the system 
    \begin{equation}
        \frac{d}{dz}Y= B(z) Y 
    \end{equation}
    \[
    B(z)=\begin{pmatrix}
            0 & 1 & 0 & \ldots & 0 \\
            0 & 0 & 1 & \ldots & 0 \\
            \vdots & &\ddots & & 1\\
            b_{1}(z) & & b_j(z) & \ldots & b_{d-1}(z)
        \end{pmatrix}, \quad Y=\begin{pmatrix}
            \psi \\
            \psi ' \\
            \vdots \\
            \psi^{(d-1)}
        \end{pmatrix}
    \]

@@

and $-w^{-2}B(1/w)$ has a simple pole at $w=0$ (i.e. $z=\infty$). Then the formal system of solutions is of the form 
\[\psi_j(w)=e^{-\alpha_j/w} w^{\tau_j} \tilde{f}_j(w)\]
hence according to \cite[Definition 3.3.2]{diverg-resurg--ii}, $w=0$ is irregular.
\par
\end{verify}
We can find holomorphic solutions of the equation $\mathcal{P}\Phi = 0$ by taking the Borel sums of formal trans-monomial solutions. However, this only works when there is a coincidence between \begin{revised}the\end{revised} exponential factor $e^{-\alpha z}$ in the formal solution, the base point $\zeta = \alpha$ we use for Borel summation, and the characteristic equation $P(-\alpha) = 0$. Why?

A first clue is the observation that every solution we get from Borel summation is, by definition, the Laplace transform $\Phi = \laplace_{\zeta,\alpha}^\theta \phi$ of a function \begin{revised} $\phi$ on\end{revised} the position domain. In fact, the differential equation $\mathcal{P}\Phi = 0$ is equivalent to an integral equation $\hat{\mathcal{P}}_\alpha \phi = 0$.
